\documentclass[12pt]{article}

% Remove page numbering
\pagestyle{empty}

% Allow hyperlinks
\usepackage{hyperref}

% Set hyperlink color and style
\hypersetup{colorlinks,breaklinks,urlcolor=blue,linkcolor=blue}

% Don't indent paragraphs
\setlength{\parindent}{0pt}

\begin{document}

%---------------------------------------
% Heading
%---------------------------------------

\begin{center}
\Huge{Michele Lindroos} \\
\normalsize{\today}
\end{center}

%---------------------------------------
% Personal Data
%---------------------------------------

\section*{Personal Data}
\begin{tabular}{rl}
Place and Date of Birth & Finland, June 25, 1987\\
Address & Saukonpaadenranta 4 B 32, Helsinki\\
Phone & +358 40 52 54 920\\
E-mail & \href{mailto:michele.lindroos@gmail.com}{michele.lindroos@gmail.com}\\
GitHub & \href{https://github.com/keelefi}{keelefi}
\end{tabular}

%---------------------------------------
% Work Experience
%---------------------------------------

\section*{Work Experience}

\large{January, 2022 - Current, Omoroi}\\
\normalsize{Product Development Specialist.}\\
\\
\normalsize{Customer assignment. Build systems architecturing. Build and test reliability improvements.}\\
\\
\normalsize{Expertise: Bazel, autoconf, BuildFarm, ansible}\\

\large{January, 2020 - December, 2021, Omoroi}\\
\normalsize{Product Development Specialist.}\\
\\
\normalsize{Customer assignment. Cloud product line architecturing. Continuous Delpoyment machinery building.}\\
\\
\normalsize{Expertise: github actions, terraform, AWS, Kubernetes, ansible, OAuth 2.0}\\

\large{June, 2018 - January, 2020, Omoroi}\\
\normalsize{Product Development Specialist.}\\
\\
\normalsize{Customer assignment. Middleware architecturing, development and support.}\\
\\
\normalsize{Expertise: systemd, bitbake, python, bash}\\

\large{June, 2017 - June, 2018, F-Secure}\\
\normalsize{Senior Software Developer, Corporate Linux Products.}\\
\\
\normalsize{Developing Linux products.}\\
\\
\normalsize{Expertise: HTTP, LDAP, AD, Kerberos.}\\

\large{January, 2015 - May, 2017, LM Ericsson}\\
\normalsize{Experienced Software Developer.}\\
\\
\normalsize{Developing solutions for cloud-based signal processing. Linux distribution integration. Continuous Integration machinery building.}\\
\\
\normalsize{Expertise: Linux, Docker, Jenkins, OpenStack.}\\

\large{June, 2012 - December, 2014, LM Ericsson}\\
\normalsize{Software Developer.}\\
\\
\normalsize{Developing low-latency and low-memory solutions for signal processing in embedded environment. Working on own Master's Thesis.}\\

\large{Summer 2011, Aalto University, Acoustics Laboratory}\\
\normalsize{Research assistant at Research group of Paavo Alku (speech
processing).}\\

\large{Summer 2010, Aalto University, Acoustics Laboratory}\\
\normalsize{Research Assistant at Research group of Ville Pulkki (spatial
sound).}\\

\large{Autumn 2008 - Spring 2011, Aalto University, Laboratory of Mathematics}\\
\normalsize{Teacher of Basic Engineering Mathematics.}\\

\large{Spring 2008 - Autumn 2009, Oy Elmorex Ltd}\\
\normalsize{System Developer.}\\

%---------------------------------------
% Education
%---------------------------------------

\section*{Education}

\large{Master of Science (Tech.), Aalto University 2014}\\
\normalsize{
Study Programme: Telecommunications\\
\\
Master's Thesis:
\href{https://aaltodoc.aalto.fi/bitstream/handle/123456789/14402/master_
Lindroos_Michele_2014.pdf?sequence=1}
{Task Scheduling in Multicore Conversational Speech Processing Systems}
}

%---------------------------------------
% Programming Languages
%---------------------------------------

\section*{Programming Languages}

\begin{tabular}{ll}
C & Excellent\\
C++ & Very Strong\\
Lisp (Scheme) & Strong\\
JavaScript (Node.js) & Strong\\
Python & Strong\\
Java & Strong\\
(Object) Pascal & Strong\\
(Visual) Basic & Mediocre
\end{tabular}

%---------------------------------------
% Scripting Languages
%---------------------------------------

\section*{Scripting Languages}

\begin{tabular}{ll}
PHP & Strong\\
Tcl/Tk/Expect & Strong\\
JavaScript & Mediocre\\
Bash & Mediocre\\
Groovy & Basics\\
\end{tabular}

%---------------------------------------
% Assembly Languages
%---------------------------------------

\section*{Assembly Languages}

\begin{tabular}{ll}
MIPS & Mediocre\\
Freescale DSP & Mediocre\\
x86 (GAS) & Basics\\
ARM & Basics\\
\end{tabular}

%---------------------------------------
% Languages
%---------------------------------------

\section*{Languages}
\begin{tabular}{ll}
Finnish & Excellent\\
Swedish & Excellent\\
English & Strong\\
Italian & Mediocre\\
\end{tabular}

\end{document}
